The Blue Obelisk five years on

### 2011-03-04 paper.tex
Test commit
Added test on struct stds

%%%%%%%%%%%%%%%%
%% Background %%
%%
\section*{Background}
The Blue Obelisk group was established in 200X at the 2XXth National Meeting of the American Chemistry Society as a response to the lack of open data, open standards and open source (ODOSOS) in chemistry. While other scientific disciplines such as physics, biology and astronomy (to name a few) were embracing new ways of doing science and reaping the benefits of community efforts, there was little if any innovation in the field of chemistry and scientific progress was actively hampered by the lack of access to data and tools.

@@

@@

Structure Normalisation

>>>>

%%%%%%%%%%%%%%%%
%% Background %%
%%
\section*{Background}
The Blue Obelisk group was established in 2005 at the
229\textsuperscript{th} National Meeting of the American Chemistry
Society as a response to the lack of open data, open standards and
open source (ODOSOS) in chemistry. While other scientific disciplines
such as physics, biology and astronomy (to name a few) were embracing
new ways of doing science and reaping the benefits of community
efforts, there was little if any innovation in the field of chemistry
and scientific progress was actively hampered by the lack of access to
data and tools.

@@

Pistoia Alliance (and others?) should be mentioned at this point

@@

A core requirement for chemical structure databases and chemical
registration systems in general is the notion of structure
standardization.  That is,  for a given input structure, multiple
representations should be converted to one canonical form. 
Structure canonicalization routines partially address this aspect,
converting multiple alternative topologies to a single canonical
form. However, the problem of standardization is broader than just
topological canonicalization. Features that must be considered include
\begin{itemize}
\item topological canonicalization
\item handling of charges
\item tautomer enumeration and canonicalization
\item normalization of functional groups
\end{itemize}
Currently, most of the individual components of a ``standardization
pipeline'' can be implemented using BO tools. The larger problem is
that there is no agreed upon list of steps for a standardization
process. While some specifications have been published (e.g., Pubchem)
and some standardization services and tools are available (Pubchem
provides an online service to standaridize molecules and the NCGC
provides a stand alone tool) each group has their own set of rules. A
common reference specification for standardization would be of immense
value in interoperability between structure repositories as well as
between toolkits (though the latter is still confounded by differences
in lower level cheminformatic features such as aromaticity models).
